---
title: "Practice Heat Shocks"
output:
  pdf_document:
    toc: yes
  html_document:
    toc: yes
  word_document:
    toc: yes
---

# Libraries
```{r}
library(lubridate)
library(dplyr)
library(ggplot2)
library(tidyr)
library(data.table)
```

# Obtaining the data from Github
```{r}
dat<-fread("https://raw.githubusercontent.com/HannahHChu/Proteome_stability_project/master/Data/2018-06-21_thermal_assays_masterdatasheet.csv")

#glimpse(dat)
```


# Changing MIN:SEC to minutes
```{r}
rtime<- dat$kd_time
time<-lubridate::minute(ms(rtime))+lubridate::second(ms(rtime))/60
#time

#Adding new column of correct time
dat$time<-time
```

# Creating the Data Frame
```{r}
df<-data.frame(dat$kd_temp, dat$time, dat$treatment, dat$line, dat$sex)

#filtering out the non-static practice trials
staths<- df%>%
          filter(dat$treatment == "static")
```

# ANOVA
```{r} 
fit<-aov(dat.time ~ dat.kd_temp*dat.line, staths)
summary(fit)
```
ANOVA was done to determine whether there were significant differences in KD time at each temperature. The ANOVA doesn't indicate a relationship between the different lines and KD temperature. The only significant variable is KD temperature, which means we can reject the null hypothesis that there are equal means for KD temperature.

# Figures

## Overview of static HS
```{r}
staticoverview <- ggplot(staths,aes(x=dat.kd_temp,y=dat.time))+geom_point()+
  labs(x = "KD Temperature (ºC)", y = "KD time (min)") + theme(
        axis.ticks.x=element_blank(),legend.position="bottom",
        axis.ticks.y=element_blank(),panel.background = element_blank(),
        panel.grid.major = element_blank(),panel.grid.minor =
          element_blank(),axis.text=element_text(size=9),text=element_text(size=15))+geom_smooth(method="auto", se=F)
staticoverview 
```
Overall, it looks like as flies reach their upper thermal limit, their tolerance range narrows. The shape of the graph suggests that there is more variation at lower temperatures. 

## Static HS based on lines
```{r}
p<- ggplot(staths,aes(x=dat.kd_temp,y=dat.time, colour=dat.line))+geom_point()+
  labs(x = "KD Temperature (ºC)", y = "KD time (min)") + theme(
        axis.ticks.x=element_blank(),legend.position="bottom",
        axis.ticks.y=element_blank(),panel.background = element_blank(),
        panel.grid.major = element_blank(),panel.grid.minor =
          element_blank(),axis.text=element_text(size=9),text=element_text(size=15))+geom_smooth(method="auto", se=F)
fig <- p + scale_colour_discrete(name = "lines")
fig
```


## Slow ramp HS based on lines
```{r}
slowdat <- df%>%
  filter(dat$treatment == "slow", dat$kd_temp > "37")

q<- ggplot(slowdat,aes(x=dat.kd_temp,y=dat.time, colour=dat.line))+geom_point()+
  labs(x = "KD Temperature (ºC)", y = "KD time (min)") + theme(
        axis.ticks.x=element_blank(),legend.position="bottom",
        axis.ticks.y=element_blank(),panel.background = element_blank(),
        panel.grid.major = element_blank(),panel.grid.minor =
          element_blank(),axis.text=element_text(size=9),text=element_text(size=15))
slowfig <- q + scale_colour_discrete(name = "lines")
slowfig
```

## Fast ramp HS based on line
```{r}
fastdat <- df%>%
  filter(dat$treatment == "fast")

r<- ggplot(fastdat,aes(x=dat.kd_temp,y=dat.time, colour=dat.line))+geom_point()+
  labs(x = "KD Temperature (ºC)", y = "KD time (min)") + theme(
        axis.ticks.x=element_blank(),legend.position="bottom",
        axis.ticks.y=element_blank(),panel.background = element_blank(),
        panel.grid.major = element_blank(),panel.grid.minor =
          element_blank(),axis.text=element_text(size=9),text=element_text(size=15))
fastfig <- r + scale_colour_discrete(name = "lines")
fastfig 
```

# Session Info
```{r}
sessionInfo()
```